Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-02 analysis/paper/results.Rmd
started Discussion section

>>>>

Some hotspot scatter plots show points with both high pleiotropy test statistics and high mediation 
LOD differences. Closer investigation of these points reveals that, for a given hotspot, they 
include a single local trait. For example, multiple pairs with local trait *Tmem130* have high 
mediation LOD differences and high pleiotropy test statistics. This may indicate that our QTL scan 
region was too narrow to encompass the entirety of the *Tmem130* peak.
